Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-09-22 R0V0.tex
Better explanation to the number of monomials to be optimized

When $N\geq6$ and $Y$ is a full matrix with elements described by polynomials, the MI \eqref{eq:MI formulation} could not be solved with the optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek running on an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b. A reason for this issue is the dependence of each element of the matrix $Y$ on the variable $q$. Another reason is the need to verify if the matrix \eqref{eq:MI formulation} is negative definite. When no structural constraints are imposed on $Y$, this verification can lead to
\begin{equation*}
\left(\sum_{i=1}^N\begin{pmatrix}
n_i+d\\ d
\end{pmatrix}\right)^2
\end{equation*}
equations to be solved. This motivates the approach proposed in this paper.

>>>>

When $N\geq6$ and $Y$ is a full matrix with elements described by polynomials, the MI \eqref{eq:MI formulation} could not be solved with the optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek running on an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b. A reason for this issue is the dependence of each element of the matrix $Y$ on the variable $q$. Another reason is the need to verify if the matrix \eqref{eq:MI formulation} is negative definite. For instance, when  polynomials with degree $d$ are employed, the number of monomials to be optimized in the $(i,j)$ position the matrix $T$ is
\begin{equation*}
		\begin{pmatrix}
n+d\\ d
\end{pmatrix}\;.
\end{equation*}
Consequently, when no structural constraints are imposed on $Y$, this verification can lead to
\begin{equation*}
N^2\begin{pmatrix}
n+d\\ d
\end{pmatrix}^2
\end{equation*}
equations to be solved. This motivates the approach proposed in this paper.
